Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-28 paper-v1.tex
Privacy

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach.

@@

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol security layer via zkANTS.

\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{Private transactions.}To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol. In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Future developments will investigate viable solutions, for scaling the system, like ZK-ZK Rollup by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.

\subsubsection{Tokenomics}
AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of the Ants-Review Community). zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

>>>>

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs and homomorphic encryption (see § Privacy in 3.2).

@@

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.

\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption to validate encrypted transactions.
\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
\newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of the Ants-Review Community). zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
